---
title: "MovieLens Project: Recommender System Capstone Project - Code"
author: "Dennier Agreda"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
    highlight: pygments
    keep_tex: true
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center', cache=FALSE, cache.lazy = FALSE)
```

```{r, installing, echo=FALSE, warning=FALSE, message=FALSE}
# This instruction only applies when you do not have install required libraries
if(!require(tidyverse)) install.packages("tidyverse") 
if(!require(kableExtra)) install.packages("kableExtra")
if(!require(tidyr)) install.packages("tidyr")
if(!require(tidyverse)) install.packages("tidyverse")
if(!require(stringr)) install.packages("stringr")
if(!require(forcats)) install.packages("forcats")
if(!require(ggplot2)) install.packages("ggplot2")
if(!require(caret)) install.packages("caret")

```

```{r, loading, echo=FALSE, message=FALSE, warning=FALSE}
# Loading libraries
library(dplyr)
library(tidyverse)
library(kableExtra)
library(tidyr)
library(stringr)
library(forcats)
library(ggplot2)
library(caret)

# MovieLens 10M dataset:
# https://grouplens.org/datasets/movielens/10m/
# http://files.grouplens.org/datasets/movielens/ml-10m.zip
dl <- tempfile()
download.file("http://files.grouplens.org/datasets/movielens/ml-10m.zip", dl)
ratings <- read.table(text = gsub("::", "\t", readLines(unzip(dl, "ml-10M100K/ratings.dat"))),
                      col.names = c("userId", "movieId", "rating", "timestamp"))
movies <- str_split_fixed(readLines(unzip(dl, "ml-10M100K/movies.dat")), "\\::", 3)
colnames(movies) <- c("movieId", "title", "genres")
movies <- as.data.frame(movies) %>% mutate(movieId = as.numeric(levels(movieId))[movieId],
                                           title = as.character(title),
                                           genres = as.character(genres))
movielens <- left_join(ratings, movies, by = "movieId")
# Validation set will be 10% of MovieLens data
set.seed(1)
test_index <- createDataPartition(y = movielens$rating, times = 1, p = 0.25, list = FALSE)
edx <- movielens[-test_index,]
temp <- movielens[test_index,]
# Make sure userId and movieId in validation set are also in edx set
validation <- temp %>% 
  semi_join(edx, by = "movieId") %>%
  semi_join(edx, by = "userId")
# Add rows removed from validation set back into edx set
removed <- anti_join(temp, validation)
edx <- rbind(edx, removed)
rm(dl, ratings, movies, test_index, temp, movielens, removed)


```

# Executive Summary

## Dataset Explanation

Datasets have six features, these will be described above:

- **userId** *integer* contains the unique identification number for each user.
- **movieId** *numeric* contains the unique identification number for each movie.
- **rating** *numeric* contains the rating of one movie by one user. Ratings are made on a 5-Star scale with half-star increments.
- **timestamp** *integer* contains the time-stamp for one specific rating provided by one user.
- **title** *character* contains the title of each movie including the year of the release.
- **genres** *character* contains a list of pipe-separated of genre of each movie.

# Exploratory Data Analysis



```{r, head, echo=FALSE}
head(edx) %>%
   kable(caption = 'First values from dataset EDX') %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                 position = "center",
                 font_size = 10,
                 full_width = FALSE)
```

## Missing values count

## Feature Engineering

## Some Statistics

# Models

## Naive Mean Model

## Bias Effects Approach

### Movie's Effects - Approach Model

### User's Effects -  Approach Model

### Genre's Effects - Aproach Model

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
